Carbon bias

### 2015-07-15 Rmd/carbon-bias.Rmd
much of the way through yield-bias.Rmd analysis. Added new function disaggregate_rast_list. Various tweaks and nudges.

    # stack raster bins, cropland bins, and landcover set
    s <- stack(list("bin" = gti_bins[[x]], "wgt" = area_wgts[[x]][[1]], 
                    "mask" = lc_union[[x]][[y]], c_pct_diff[[x]][[y]]))
    DT <- na.omit(agroEcoTradeoff::as.data.table.raster(s))
    setkey(DT, "bin")
    # indexing columns
    #front1 <- data.table("bin" = rep("all", 6), "N" = rep(nrow(DT), 6))
    #front2 <- data.table("bin" = rep("abs", 6), "N" = rep(nrow(DT), 6))
    # stats, overall means
    #m <- cbind(bvals, DT[mask == 1, lapply(.SD, bfn, wgt), .SDcols = nms1])
    #ma <- cbind(bvals, DT[mask == 1, lapply(.SD, bfna, wgt), .SDcols = nms1])
    # stats per bin
    #b <- cbind(bvals, 
    #           DT[mask == 1, lapply(.SD, bfn, wgt), by = bin, .SDcols = nms1])
    #ba <- cbind(bvals, 
    #            DT[mask == 1, lapply(.SD, bfna, wgt), by = bin, .SDcols = nms1])    
    # output
    #odt <- rbind(cbind(front1, mu), cbind(front2, muabs), 
    #             binl[bin][, bin := paste0("a", bin)], 
    #             binl[binabs][, bin := paste0("b", bin)])[, wgt := NULL]

@@

# Statistics from non-croplands areas included in means, for supplementals
nmrepl <- cbind(snms, lcnms)
mu0[, c(lev_vec) := lapply(.SD, round), .SDcols = lev_vec]
mu0a[, c(lev_vec) := lapply(.SD, round), .SDcols = lev_vec]
mu0[, V1 := nmrepl[match(V1, nmrepl), 2]]
mu0a[, V1 := nmrepl[match(V1, nmrepl), 2]]
mu0s <- rbind(cbind(stat = "actual", mu0), cbind(stat = "absolute", mu0a))
mu0s_xtab <- xtable::xtable(mu0s)
print(mu0s_xtab, type = "latex", file = "paper/figures/C-bias-mean-all-SA.tex")

# Statistics from non-croplands areas included in means, for supplementals
nmrepl <- cbind(snms, lcnms)
mu[, c(lev_vec) := lapply(.SD, round), .SDcols = lev_vec]
mua[, c(lev_vec) := lapply(.SD, round), .SDcols = lev_vec]
mu[, V1 := nmrepl[match(V1, nmrepl), 2]]
mua[, V1 := nmrepl[match(V1, nmrepl), 2]]
mus <- rbind(cbind(stat = "actual", mu), cbind(stat = "absolute", mua))
mus_xtab <- xtable::xtable(mus)
print(mu0s_xtab, type = "latex", 
      file = "paper/figures/C-bias-mean-cropland-SA.tex")

@@

#### Main text version of mean carbon bias against scale
```{r, eval=FALSE}
alph <- c(225, 75)
#Ccols <- brewer.pal(n = 7, name = "Greys")
LC2 <- c(LC[-grep("second|grass", LC)], "all")
# xax <- seq(0, 7, 6 / (length(yax) - 2)); length(xax)
x <- c(0, 3, 6, 9, 12, 15)
w <- 3 / 8
xo <- (cumsum(rep(w, 8)) - w / 2)[-c(2, 4, 6, 8)]
#x + xo[j] + o[k]
xa <- sapply(x, function(x) x + xo)
mutype <- c("mua", "mu")

@@

@@

gti_

>>>>

    # stack raster bins, cropland bins, and landcover set
    s <- stack(list("bin" = gti_bins[[x]], "wgt" = area_wgts[[x]][[1]], 
                    "mask" = lc_union[[x]][[y]], c_pct_diff[[x]][[y]]))
    DT <- na.omit(as.data.table.raster(s))
    setkey(DT, "bin")
    # indexing columns
    #front1 <- data.table("bin" = rep("all", 6), "N" = rep(nrow(DT), 6))
    #front2 <- data.table("bin" = rep("abs", 6), "N" = rep(nrow(DT), 6))
    # stats, overall means
    #m <- cbind(bvals, DT[mask == 1, lapply(.SD, bfn, wgt), .SDcols = nms1])
    #ma <- cbind(bvals, DT[mask == 1, lapply(.SD, bfna, wgt), .SDcols = nms1])
    # stats per bin
    #b <- cbind(bvals, 
    #           DT[mask == 1, lapply(.SD, bfn, wgt), by = bin, .SDcols = nms1])
    #ba <- cbind(bvals, 
    #            DT[mask == 1, lapply(.SD, bfna, wgt), by = bin, .SDcols = nms1])    
    # output
    #odt <- rbind(cbind(front1, mu), cbind(front2, muabs), 
    #             binl[bin][, bin := paste0("a", bin)], 
    #             binl[binabs][, bin := paste0("b", bin)])[, wgt := NULL]

@@

@@

#### Main text version of mean carbon bias against scale
```{r, eval=FALSE}
alph <- c(225, 40)
#Ccols <- brewer.pal(n = 7, name = "Greys")
LC2 <- c(LC[-grep("second|grass", LC)], "all")
# xax <- seq(0, 7, 6 / (length(yax) - 2)); length(xax)
x <- c(0, 3, 6, 9, 12, 15)
w <- 3 / 8
xo <- (cumsum(rep(w, 8)) - w / 2)[-c(2, 4, 6, 8)]
#x + xo[j] + o[k]
xa <- sapply(x, function(x) x + xo)
mutype <- c("mua", "mu")

@@

#### Supplementary mean bias tables
```{r, eval=FALSE}
# Statistics from non-croplands areas included in means, for supplementals
nmrepl <- cbind(snms, lcnms)
mu0[, c(lev_vec) := lapply(.SD, round), .SDcols = lev_vec]
mu0a[, c(lev_vec) := lapply(.SD, round), .SDcols = lev_vec]
mu0[, V1 := nmrepl[match(V1, nmrepl), 2]]
mu0a[, V1 := nmrepl[match(V1, nmrepl), 2]]
mu0s <- rbind(cbind(stat = "actual", mu0), cbind(stat = "absolute", mu0a))
mu0s_xtab <- xtable::xtable(mu0s)
print(mu0s_xtab, type = "latex", file = "paper/figures/C-bias-mean-all-SA.tex")

# Statistics from non-croplands areas included in means, for supplementals
nmrepl <- cbind(snms, lcnms)
mu[, c(lev_vec) := lapply(.SD, round), .SDcols = lev_vec]
mua[, c(lev_vec) := lapply(.SD, round), .SDcols = lev_vec]
mu[, V1 := nmrepl[match(V1, nmrepl), 2]]
mua[, V1 := nmrepl[match(V1, nmrepl), 2]]
mus <- rbind(cbind(stat = "actual", mu), cbind(stat = "absolute", mua))
mus_xtab <- xtable::xtable(mus)
print(mu0s_xtab, type = "latex", 
      file = "paper/figures/C-bias-mean-cropland-SA.tex")
```

@@
